High-order dynamic neural correlations reflect naturalistic processing in humans

### 2019-05-06 paper/main.tex
WIP paper

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods_fig}
  \caption{\textbf{Computing higher order correlations. } Correlations
  are computed then approximated to the same size as original data.
  This process is repeated to computer }
  \label{fig:methods_fig}
\end{figure}

@@

To generate synthetic data from a dynamically changing covariance
matrix (ramping covariance matrix Fig.~\ref{fig:synthetic_data},  C.),
we generated two random covariance
matrices, $K_{1}$ and $K_{2}$.  We then computed a covariance matrix
for each of the 300 timepoint, $K(t)$ 
by taking the linearly spaced weights ($w$) of the two random matrices, 
\begin{align}
K(t) = w(t) * K_{1} + 1 - w(t) *  K_{2}
\end{align}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
  \caption{\textbf{Dynamic correlation recovery with synthetic data.
      a.Recovery using a constant dataset.} Using constant dataset,
    how well can we recover using different
    kernels. \textbf{b. Recovery using random dataset.}
    \textbf{c. Ramping recovery.}  \textbf{d. Block recovery} blah}
  \label{fig:synthetic_data}
\end{figure}

@@

We applied timecorr, using delta and gaussian kernels
Fig.~\ref{fig:weights}) to each of these 
synthetic datasets, then correlate each recovered
correlation matrix with the ground truth.  Explore how recovery varies
with the kernel and the specific structure of the data
(e.g. slow changes as in the ramping dataset, versus rapid changes as
in the block dataset).

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/corrmats.pdf}
  \caption{\textbf{Inter-subject correlations by order.
      a. Inter-subject correlation heatmaps by order.}  Heatmaps for
    each order of how correlated each subject is with every other
    subject grouped by condition (intact (I), paragraph
    (P), word (W),
    and rest (R)). \textbf{b. Mean correlation for each
      condition by order.}
   Bar heights indicate inter-subject correlations by conditon for each order.}
  \label{fig:corrmats}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}
\begin{itemize}

>>>>

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/methods_fig}
  \caption{\textbf{Computing higher order correlations. } Dynamic
    correlations
  are computed then approximated to the same size as original data
  using dimensionality reduction.
  This process is repeated, and can be used to compute up to any
  arbitrary order with compuations scaling linearly (as opposed to exponentially) with order. }
  \label{fig:methods_fig}
\end{figure}

@@

To generate synthetic data from a dynamically changing covariance
matrix (Ramping, Fig.~\ref{fig:synthetic_data},  C.),
we generated two random covariance
matrices, $K_{1}$ and $K_{2}$.  We then computed a weighted average covariance matrix
for each of the 300 timepoint, $K(t)$, 
by taking the linearly spaced weights ($w$) of the two random matrices, 
\begin{align}
K(t) = w(t) * K_{1} + (1 - w(t)) *  K_{2},
\end{align}
and for each of the 300 timepoints sampled from a
Gaussian distribution centered on $K(t)$. We also explored
recovery by comparing this ramping synthetic data to only the first random covariance matrix $K_{1}$
(First, Fig.~\ref{fig:synthetic_data},  C.) and using only the last
random covariance matrix $K_{2}$ (Last, Fig.~\ref{fig:synthetic_data},
C.).

For the synthetic data containing block structure, we followed the same
process of creating synthetic data sampled from a constant covariance
matrix (see above) but sampled from a new random covariance matrix
after each 60 consecutive timepoints.  We then pieced the blocks together
to create a sythetic dataset with 300 total timepoints but drawn from
5 separate covariance matrices. We then compared recovery using the
total dataset (All, Fig.~\ref{fig:synthetic_data},  D.) or limiting to
the block specific covariance matrix (Block 1-5, Fig.~\ref{fig:synthetic_data},  D.).

(Fig.~\ref{fig:synthetic_data},  D.) ,

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{figs/synthetic_data.pdf}
  \caption{\textbf{Dynamic correlation recovery with synthetic data. } Using synthetic data containing different
    underlying correlational structure,
   we test how well we can recover using two kernels (delta and gaussian,
    width = 10).  We plot recovery using of datasets containing the
    following underlying structure:
    \textbf{a. Constant. b. Random. c. Ramping.  d. Block.}}
  \label{fig:synthetic_data}
\end{figure}

@@

We applied timecorr, using delta and gaussian kernels
Fig.~\ref{fig:weights}) to each of these 
synthetic datasets, then correlate each recovered
correlation matrix with the ground truth.  We explore how recovery varies
with the kernel and the specific structure of the data
(e.g. slow changes as in the ramping dataset, versus rapid changes as
in the block dataset).

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}

\begin{itemize}
